Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/model.tex
Minor edit.

\item an exploration-separated algorithm that in each round, \emph{explores} with probability $\eps$: chooses an arm independently and uniformly at random, and with the remaining probability \emph{exploits} according to \DG. We call it ``dynamic epsilon-greedy", \DEG in short.\gaedit{\footnote{For our experiments, we fix $\eps = 0.05$. Our pilot experiments showed that different $\eps$ did not qualitatively change the results.}}

@@

\item \emph{Uniform instance}: the mean reward of each arm is drawn independently and uniformly from $[0.25, 0.75]$.
\item \emph{Heavy-tail instance}: the mean reward of each arm is drawn independently from $\Beta(.6,.6)$ distribution.%
    \footnote{This distribution has substantial ``tail probabilities".}
\end{enumerate}
We argue that these MAB instances are (somewhat) representative. Consider the ``gap" between the best and the second-best arm, an essential parameter in the literature on MAB. The ``gap" is fixed in Needle-in-Haystack, spread over a wide spectrum of values under the Uniform instance, and is spread but  focused on the large values under the Heavy-Tail instance. We also ran smaller experiments with versions of these instances, and achieved similar qualitative results.

>>>>

\item an exploration-separated algorithm that in each round, \emph{explores} with probability $\eps$: chooses an arm independently and uniformly at random, and with the remaining probability \emph{exploits} according to \DG. We call it ``dynamic epsilon-greedy", \DEG in short.\gaedit{\footnote{Throughout, we fix $\eps = 0.05$. Our pilot experiments showed that different $\eps$ did not qualitatively change the results.}}

@@

\item \emph{Uniform instance}: the mean reward of each arm is drawn independently and uniformly from $[\nicefrac{1}{4}, \nicefrac{3}{4}]$.
\item \emph{Heavy-tail instance}: the mean reward of each arm is drawn independently from $\Beta(.6,.6)$ distribution (which is known to have substantial ``tail probabilities").
\end{enumerate}
We argue that these MAB instances are (somewhat) representative. Consider the ``gap" between the best and the second-best arm, an essential parameter in the literature on MAB. The ``gap" is fixed in Needle-in-Haystack, spread over a wide spectrum of values under the Uniform instance, and is spread but  focused on the large values under the Heavy-Tail instance. We also ran smaller experiments with versions of these instances, and achieved similar qualitative results.
